Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-31 automatica/paper.tex
overall paper

%\runtitle{Automated Synthesis of Safe Digital Controllers}  % Running title for regular 
                                              % papers but only if the title  
                                              % is over 5 words. Running title 
                                              % is not shown in output.

@@

@@

Equation~\eqref{eq:ode1} is 
%soundly 
discretized in time~\cite{middleton1990digital,van1978computing} with constant sampling intervals, 
each of duration $T_s$ (the sample time), 
into the difference equation
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
\end{align} 
where 
$\mat{A}_d=e^{\mat{A}T_s}$ and 
$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
\reply{This time discretization introduces errors that fall outside the scope of this work.}
%\note{shall we add a note on time discretization errors? namely that we disregard them? }

>>>>

@@

\titlerunning{Automated Synthesis of Safe Digital Controllers}  % Running title for regular 
                                              % papers but only if the title  
                                              % is over 5 words. Running title 
                                              % is not shown in output

@@

Equation~\eqref{eq:ode1} is 
%soundly 
discretized in time~\cite{middleton1990digital,van1978computing} with constant sampling intervals, 
each of duration $T_s$ (the sample time), 
into the difference equation
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
\end{align} 
where 
$\mat{A}_d=e^{\mat{A}T_s}$ and 
$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
We assume that specifications on the model concern \eqref{eq:plant}, 
and plan to devise controllers $\vec{u}_k$ to meet them. 
(The more general problem of synthesising controllers $u(t)$ for \eqref{eq:ode1} fall outside the scope of the present work.)
